---
title: "Case Study Workflow"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose

In this document we conduct the analysis of the empirical data on ecosystem service supply and demand to test the hypotheses generated by the simulations. The data for the case studies we analyse are available here: https://portal.idiv.de/owncloud/index.php/apps/files/?dir=/sLandServ/manuscripts/framework_ms/data&fileid=35467426

1. Deer hunting in the Monteregie, Quebec  

## Required libraries

library(sLandserv)
library(sf)
library(tidyverse)

## Deer hunting

First we load the supply, demand, and Municipality data. Note here that the deer habitat and demand data are intersected with the Municipalities boundaries so that areas in different Municipalities are treated as separate nodes in the networks  

```{r setup, eval=TRUE}
DeerHabitat <- st_read("data/deer/int_deer_forest_rem5_munic.shp")
Demand <- st_read("data/deer/int_demand_munic.shp")
Munics <- st_read("data/deer/municipalities_clean.shp")
```

Then  we need to
